
\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{parskip}

% Custom section formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{1.5em}{0.8em}

% Custom subsection formatting for job titles
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}
\titlespacing*{\subsection}{0pt}{0.8em}{0.3em}

\renewcommand{\familydefault}{\sfdefault}
\setlength{\parskip}{0.3em}

\begin{document}

% Fixed header with Maheshwor's contact information
\begin{center}
    {\LARGE \textbf{Maheshwor Tiwari}}\\[4pt]
    \normalsize
    \href{tel:+61414032507}{0414 032 507} \,|\, 
    \href{mailto:maheshtiwari99@gmail.com}{maheshtiwari99@gmail.com} \,|\, 
    \href{https://medium.com/@maheshtwari99}{Blogs on Medium} \,|\, 
    \href{https://github.com/mahesh989}{GitHub} \,|\, 
    \href{https://public.tableau.com/app/profile/maheshwor.tiwari4503/vizzes}{Dashboard Portfolio}
\end{center}

\vspace{0.5em}
\hrule
\vspace{1em}

% Professional Summary
\section*{Professional Summary}
Experienced Data Analyst and Software Engineer with expertise in Python, machine learning, and full-stack development. Proven track record in developing data-driven solutions, building scalable applications, and improving business processes through advanced analytics and automation.

% Education Section
\section*{Education}

\textbf{Northeastern University, Khoury College of Computer Sciences                                           Boston, MA
Bachelor of Science in Computer Science | Minor: Business Administration                                May, 2027
Activities: FireByte Club (Software Team) | Knack Peer Tutor
Relevant Courses: Object Oriented Design, Financial & Data Modeling, Systems & Algorithms, Data Analysis & Manipulation}



% Experience Section
\section*{Experience}

\textbf{Meta Scifor Technologies                                                                                   Remote
AI/ML Intern                                                                        September 2024 – December 2024
• Collaborated with 5 interns and developed a movie recommendation system using Python & SQL, processing 1,000+ user interactions to generate personalized recommendations across 500+ titles.
• Enhanced the UI with ReactJS & utilized Python for data analysis, and visualization. Integrated collaborative & content-based filtering, resulting in 36% more accuracy. Used RMSE, Precision and F1 Score for error calculation; achieved 92% accuracy.}


\textbf{Rosy Blue Inc.                                                                                        Manhattan, NY
Quantitative Analyst Intern                                                               July 2024 – September 2024
• Analyzed 50+ companies using Python & SQL for investment recommendations, generating 12% returns through 3 successful trades. Built PowerBI and Plotly interactive dashboards to visualize market trends, reducing analysis time by 33%.
• Automated data pipelines with pandas, processing 11B+ financial data saving .1M annually in operations cost.
• Authored investment research reports using ML predictions, achieving 85% accuracy in price forecasting.}


\textbf{ASE Consulting                                                                                           Mumbai, India
Software Engineer Intern                                                                    May 2024 – July 2024
• Designed an E-commerce platform using ReactJS, MongoDB, featuring 1,000+ items, cart management, & secure checkout.
• Conducted beta testing to gather user feedback, enhancing functionality and user experience. Analyzed results, improving customer satisfaction and retention by 30%, and processed 200+ transactions.
• Incorporated lazy loading, code splitting, and caching techniques to achieve a 2800ms increase in speed.}



% Skills Section
\section*{Skills and Interests}
\textbf{Programming Languages:} 
Python, Java, JS, SQL, C/C++, Django, Node.js, React, AWS, PowerBI, Tableau, Excel, R, AutoCAD, Onshape, Git, Linux, PyTorch, TensorFlow, HTML/CSS, AWS, PowerBi, Tableau, Excel, R, AutoCAD, Onshape

\end{document}